preciseTAD: A machine learning framework for precise TAD boundary prediction at base level resolution

### 2020-08-15 Manuscript/manuscript.Rmd
Update supplementary legends

**Additional File 1**. An example script for applying the Arrowhead tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line. <!--Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.-->

@@

**Supplementary Table 2.** A complete list of the genomic annotations used to build the predictor space for all downstream models. The GRCh37/hg19 human genome assembly was used. “Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell Type-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).

@@

**Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively. Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation. All genomic annotations were used. Each density curve represents an individual genomic annotation.

**Supplementary Figure 2. Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.

**Supplementary Figure 3. Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.

>>>>

**Additional File 1**. An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions. <!--Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.-->

@@

**Supplementary Table 2.** A complete list of genomic annotations used to build the predictor space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).

@@

**Supplementary Figure 1.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively. Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation. Each density curve represents an individual genomic annotation (77 total).

**Supplementary Figure 2. Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.

**Supplementary Figure 3. Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
